### 2017-02-11 ResearchNotes/exps.tex
Moved experiments to this repository

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_0_CTE-UMCED-2_all}
        \label{subfig:exp_001_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_3_INF7194_2_all}
        \label{subfig:exp_001_3_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_0_CTE-UMCED-2_cud}
        \label{subfig:exp_001_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{imgs/fig_3_INF7194_2_cud}
        \label{subfig:exp_001_3_cud}
    \end{subfigure}

>>>>

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../Exps/exp_001_results/fig_0_CTE-UMCED-2_all}
        \label{subfig:exp_001_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../Exps/exp_001_results/fig_3_INF7194_2_all}
        \label{subfig:exp_001_3_all}
    \end{subfigure}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../Exps/exp_001_results/fig_0_CTE-UMCED-2_cud}
        \label{subfig:exp_001_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../Exps/exp_001_results/fig_3_INF7194_2_cud}
        \label{subfig:exp_001_3_cud}
    \end{subfigure}

### 2017-02-11 ResearchNotes/papers.tex
Moved experiments to this repository

>>>>

% =============================================================================
\subsection{\texttt{IND\_009} - Evolutionary algorithms for subgroup discovery
applied to e-learning data}

Paper is~\cite{ind_009}. Applying evolutionary algorithms to find association
rules.

Association rules are rules that link events together following the form, ``If
event $ A $ happened, the event $ B $ is likely to occur''. These are fuzzy
rules, because an event $ A $ happening doesn't necessarily imply that event $
B $ will always happen, rather, the rules give a probabilistic notion that
should be understood has, if $ A $ happened, then $ B $ will probably also
happen.

The paper talks about subgroups in the context of association rules and genetic
algorithms to learn rules from data. The classic association rules learning
algorithms, which are Apriori-SD and CN2-SD, are mentioned.

Like other papers from these authors, the usual Moodle data is shown and
several algorithms are applied over it. The results for those algorithms is
presented and discussed. The results seemed to be quite good.
